Toward an Aspect-oriented Cache Autoloading Framework with Annotation

### 2019-02-16 paper.tex
final version by Kun Ma

\def\BottomCatch{%
\vskip -10pt
\thispagestyle{empty}%
\begin{table}[b]%
\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
\\[-12pt]
Copyright \copyright\ 2016 Inderscience Enterprises Ltd. & &%
\end{tabular*}%
\vskip -10pt%
%\vskip -35pt%
\end{table}%
}

@@

@@

@@

@@

Cache is a collection of data duplicating original values stored in memory, usually for easier access. Moreover, it can reduce the server response time efficiently \cite{ma2017segment}. There are many ways to implement the cache, such as the cache based on browser, the cache based on CDN \cite{manjhi2005finding} and the cache based on applications \cite{wu2011characterization}. Relative Database Management Systems (RDBMSs) combined with the NoSQL databases is the primary solution for the cache based on server, RDBMSs are used for data persistence, in-memory NoSQL databases are used for caching.

@@

\subsection{Contributions}
In this paper, we propose an aspect-oriented cache auto load framework with annotation. Contributions of our framework are concluded as follows.

@@

\subsection{Cache Framework}
Caching of data with weak consistency can achieve transparency. Typically, the cache content is periodically refreshed. There are different levels for caching performance, namely the browser cache \cite{davison2001web}, proxy cache \cite{kumar2008new}, Content Delivery Network (CDN) cache \cite{vakali2003content}, and server level cache \cite{ma2017column}. Browser cache is closest to the end user and can speed up page loads by storing the static files, such as a single page, on user's local storage media \cite{mookerjee2002analysis}. CachePortal \cite{candan2001enabling} relies on timestamps and HTTP logs to conservatively determine which pages to invalidate. It has a unique form of weak, time-lagged consistency. Proxy caches are situated at network access points for web users \cite{kumar2008new}. Consequently, proxy caches can store documents and directly serve requests for them in the network, thereby avoiding repeated traffic to web servers. CDN is similar to proxy caching \cite{vakali2003content}. But the difference is that the servers of CDN are distributed around the users, data is obtained from the server with least delay. The disadvantage of CDN cache is that excessive consumption of resources due to continuous analysis. Proxy cache and CDN solves the problem of the local cache cannot be shared. Although some of these products implement dynamic page cache, the effects are not good. In particular, server data processing efficiency is not effectively improved. Therefore, the present mainstream of cache is server level cache.

Recently, there are some new cache frameworks. The combination of RDBMSs and in-memory NoSQL is the mainstream architecture of server cache. Several solutions are proposed such as Redis \cite{zawodny2009redis}, Memcached \cite{hafeez2017realizing}, and EhCache. RDBMSs are used to persist data, and in-memory databases are used to store high-frequency data \cite {ma2017column}. Redis performs better for high concurrency and memory consumption. As an improvement, Memcache pool is used to duplicate high-frequency data into a dedicated data pool by cache access frequency and cache expired cost \cite{nishtala2013scaling}. This feature is achieved by the time of the cache analysis by some dedicated servers.

There are some optimizations of cache frameworks. For example, the performance of distributed storage with disks is studied \cite{scheuermann1998data}. Another data-aware cache framework (Dache) using MapReduce is proposed \cite{zhao2014dache}. In Dache, tasks submit their intermediate results to the cache manager. A task queries the cache manager before executing the actual computing work. The cache manager of ACALFA is a general framework that supports these cache frameworks.

@@

%\section*{Acknowledgement}
%The project is funded in part by the National Institutes of Health, under Grant No. 5R01CA136535.

>>>>

\def\BottomCatch{%
\vskip -10pt
\thispagestyle{empty}%
\begin{table}[b]%
\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
\\[-12pt]
Copyright \copyright\ 2019 Inderscience Enterprises Ltd. & &%
\end{tabular*}%
\vskip -10pt%
%\vskip -35pt%
\end{table}%
}

@@

\thispagestyle{plain}
\setcounter{page}{1}
\LRH{K. Ma, X. Niu, Z. Yu, and K. Ji}
\RRH{Toward an Aspect-oriented Cache Autoloading Framework with Annotation}
\VOL{19}
\ISSUE{1}
\PUBYEAR{2019}
\BottomCatch
\CLline

@@

\authorA{Kun Ma*\\
*Corresponding author}
%
\affA{Shandong Provincial Key Laboratory of Network Based Intelligent Computing,\\ University of Jinan,\\ Jinan 250022, Shandong, China \\
 E-mail: ise\_mak@ujn.edu.cn, kun.ma.cn@ieee.org\\
*Corresponding author}
%
\authorB{Xuewei Niu}
\affB{Shandong Provincial Key Laboratory of Network Based Intelligent Computing,\\ University of Jinan,\\ Jinan 250022, Shandong, China \\
E-mail: a@niuxuewei.com}

\authorC{Ziqiang Yu}
\affC{Shandong Provincial Key Laboratory of Network Based Intelligent Computing,\\ University of Jinan,\\ Jinan 250022, Shandong, China \\
E-mail: ise\_yuzq@ujn.edu.cn}

\authorD{Ke Ji}
\affD{Shandong Provincial Key Laboratory of Network Based Intelligent Computing,\\ University of Jinan,\\ Jinan 250022, Shandong, China \\
E-mail: ise\_jik@ujn.edu.cn}

@@

\REF{to this paper should be made as follows: Ma, K., Niu, X., Yu, Z., and Ji, K. (\thePUBYEAR) `Toward an Aspect-oriented Cache Autoloading Framework with Annotation', {\it Int. J. Web and Grid Services}, Vol. \theVOL, No. \theISSUE, pp.xxx\textendash xxx.}

\begin{bio}
Dr. Kun Ma received his Ph.D degree in Computer Software and Theory from Shandong University, Jinan, Shandong, China, in 2011. He is an Associate Professor in School of Information Science and Engineering, University of Jinan, China. He is the Editor-in-Chief of International Journal of Autonomic Computing, editorial board member of International Journal of Grid and Utility Computing. His research interests include situation awareness of public opinion, data intensive computing, big data management, and other big data processing technology. More information at: http://kunma.net.\vs{9}

\noindent Xuewei Niu received his bachelor degree in Computer Science and Technology from University of Jinan in 2019. His research interests include big data management and stream computing.

\noindent Ziqiang Yu received PhD degree from Shandong University, China. His research interests include streaming data processing, spatio-temporal data querying, and urban computing.

\noindent Ke Ji received PhD degree from Beijing Jiaotong University, China. His current research interests include recommender system, information retrieval and machine learning.

\end{bio}

@@

In computing, cache is a software component that stores data in memory so that future requests for that data can be served faster. A cache hit occurs reducing server response time when the requested data can be found in a cache, while a cache miss occurs when it cannot \cite{ma2017segment}. There are many examples of caches such as the cache based on browser, the cache based on CDN \cite{manjhi2005finding} and the cache based on applications \cite{wu2011characterization}. Because of performance bottlenecks from queries on Relative Database Management Systems (RDBMSs), it is now common to deploy a memory cache server in conjunction with a database to improve access performance \cite{ma2017column}.

@@

\subsection{Contributions}
In this paper, we propose an aspect-oriented cache auto load framework with annotation (ACALFA for short). Contributions of our cache framework are concluded as follows.

@@

\subsection{Cache Framework}
Caching of data with weak consistency can achieve transparency. Weak consistency of caching of data leads to the transparency of using. Typically, in-memory caching of data is periodically refreshed. There are different kinds of cache, namely the browser cache \cite{davison2001web}, proxy caching \cite{kumar2008new}, Content Delivery Network (CDN) cache \cite{vakali2003content}, and cache at server level \cite{ma2017column}. Browser cache contains records of every item viewed or downloaded while Internet surfing in local storage \cite{mookerjee2002analysis}. For example, CachePortal \cite{candan2001enabling} is to enable caching of dynamic contents generated by data-driven Web applications. It relies on timestamps and HTTP logs with weak time-lagged consistency. Proxy caching is a feature of proxy servers that stores content on the proxy server itself for web users \cite{kumar2008new}. It can store documents and directly serve requests for them in the network, thereby avoiding repeated traffic to web servers. Compared with proxy caching, CDN has a distributed architecture with low latency \cite{vakali2003content}. The disadvantage of CDN cache is that excessive consumption of resources due to continuous analysis. Both proxy caching and CDN addressed the issues that local cache cannot. Cache at server level is often the culprit of confusion and frustration when it comes to performing dynamic updates.

Recently, there are some new cache frameworks such as the integration of RDBMSs and in-memory NoSQL. There are some cache products such as Redis \cite{zawodny2009redis}, Memcached \cite{hafeez2017realizing}, and EhCache. In this solution, persist data are stored in RDBMS, and high-frequency data are stored in-memory databases {ma2017column}. Redis is an in-memory data structure store for high concurrency and memory consumption. It supports transactions and different levels of on-disk persistence, and provides high availability automatic partitioning. As an improvement, Memcached is an in-memory key-value store by cache access frequency and cache expired cost \cite{nishtala2013scaling}. It is achieved by the time of the cache analysis by distributed dedicated servers.

There are some optimizations of cache frameworks. For example, the performance of distributed storage with disks is studied \cite{scheuermann1998data}. Another data-aware cache framework (Dache) using MapReduce is proposed \cite{zhao2014dache}. In Dache, tasks submit their intermediate results to the cache manager. A task queries the cache manager before executing the actual computing work. In our paper, we propose a general management framework called ACALFA that supports these caches.

@@

\section*{Acknowledgement}
This work was supported by the National Natural Science Foundation of China (61772231), the Shandong Provincial Natural Science Foundation (ZR2017MF025), the Shandong Provincial Key R\&D Program of China (2018CXGC0706), the Science and Technology Program of University of Jinan (XKY1734 \& XKY1828), and the Project of Shandong Provincial Social Science Program (18CHLJ39).
